Beam-Helicity and Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS (v0.6)} \underline{Drafting Committee: DC90 (\today)}

### 2011-02-22 results.tex
added 2d description

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_update}
  \caption{\blue{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
the beam polarisation measurement.}}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic}
    \caption{\blue{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties.  Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}}
  \label{bca_xbjrange}
 \end{center}
\end{figure}

@@

The asymmetry amplitudes shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} were also re-binned as a function of $-t$ for three different ranges of $x_{\textrm{B}}$. There was no observed dependence of any of the amplitudes with this two dimensional binning.

>>>>

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_tc_xbjrange_eml_par13_bin6_9607_pic_update}
  \caption{\blue{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
the beam polarisation measurement.}}
  \label{bsa_xbjrange2}
 \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=15cm]{bcaplots_tc_xnjrange_eml_par13_bin6_9607_pic}
    \caption{\blue{The $A_{\textrm{C}}^{\cos(0\phi)}$, $A_{\textrm{C}}^{\cos\phi}$, $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ beam-charge asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes} from 1996 until 2007 as a function of $-t$ for three different $x_{\textrm{B}}$ ranges. The error bars (bands) represent the statistical (systematic) uncertainties.  Theoretical calculations from the model described in \cite{Kum09} are shown as solid and dashed lines. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}}
  \label{bca_xbjrange2}
 \end{center}
\end{figure}

@@

\blue{Calculations from a fit of GPDs to all existing DVCS data can be used as an alternative to comparing experimental results with existing models. The asymmetry amplitudes shown in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange}, extracted from H{\sc ermes} hydrogen data, can be described by a fit to other DVCS results. In order to provide more detailed information for future fits, in particular for the entanglement  and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. There is no observed $-t$ dependnece on any of the $A_{\textrm{LU}}$ amplitudes in either of the distinct ranges of $x_{\textrm{B}}$. Also no additional features or $-t$ dependencies are observed for the $A_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.}
